---
title: "Configuration File"
output:
 html_document:
    toc: true
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Configuration File}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The configuration YML file is the most important thing to get right in building your app. it provides the wiring instructions for building the app.R

### Dataset Configuration

Shown below is a basic example of loading 3 datasets into the shinyspring environment

-   all datasets follow the convention of ds.[ds_name].[ds_param]

-   all datasets need to atleast have a `type` and `connection` defined.

-   We currently support csv , rds , feather , parque , and you can define your own custom scheme also

```{r , eval=FALSE}

# datsets
  
  ds.misssouri.type: csv
  ds.misssouri.connection: CHART2_MO_COUNTIES.csv
 
  ds.branch_dis.type: feather
  ds.branch_dis.connection: DC_sis_dist.feather
  ds.branch_dis.subset: 10000
   ds.branch_dis.rename_cols: !expr c("branch_key" , "km100" , "km50" , "km20" , "km10" , "km5" , "km1" ,"closest_ct" , "closest_km")

  ds.iris.type: built_in
  ds.iris.connection: iris

```
